
\documentclass{harnon-cv}

\usepackage{marvosym} % For cool symbols.
\usepackage[backend=bibtex,natbib=true,style=mybibstyle,citestyle=authoryear,dashed=false,sorting=ydnt,maxbibnames=99]{biblatex} 
% sorting=ydnt: Sort by year (descending), name, title
% style=mybibstyle: remove "In:" before journal and add quotes around article title

\bibliography{myPublications} 


\DeclareNameAlias{sortname}{last-first}

	\defbibenvironment{nodis} % suppresses letters after year
  {\list
     {}
     {\setlength{\leftmargin}{\bibhang}%
      \setlength{\itemindent}{-\leftmargin}%
      \setlength{\itemsep}{\bibitemsep}%
      \setlength{\parsep}{\bibparsep}}}
  {\endlist}
  {\clearfield{extrayear}\item}
	
	
	\renewbibmacro*{volume+number+eid}{%
  \printfield{volume}%
%  \setunit*{\adddot}% DELETED
  \setunit*{\addnbspace}% NEW (optional); there's also \addnbthinspace
  \printfield{number}%
  \setunit{\addcomma\space}%
  \printfield{eid}}
\DeclareFieldFormat[article]{number}{\mkbibparens{#1}}



	% personal details
	\author{Susan Wei}  % OR - \yourname{My Name}
	\yournumber{\Telefon\ +61 3 9013 5231}
	\youremail{\Letter\ \href{mailto:susan.wei@unimelb.edu.au}{susan.wei\textrm{@}unimelb.edu.au}}
	\youraddress{School of Mathematics and Statistics \\
		Room 109, Old Geology South
University of Melbourne \\
Victoria 3010\\
Australia}
	%\yourwebsite{http://sph.umn.edu/faculty1/bio/name/susan-wei/}
	
	\recenthistory{Research interests: statistics, machine learning, deep learning}
	
	\begin{document}
	
\setlength{\bibitemsep}{\baselineskip}

		\maketitle
		
		%%% 
		\addheadertext{Education}
		\starttimeline 
			%%
			\timelineitem{2014}{
							Ph.D., Statistics \\ 
							University of North Carolina at Chapel Hill \\ 
							Advisors: Michael R. Kosorok and J.S. Marron  							
			}
			\timelinespacer
			%%
			\timelineitem{2009}{
							B.A., Mathematics with Honors\\ 
							University of California at Berkeley \\ 
						  Study abroad: Film Studies, Cambridge University, Summer 2005
			}
			\stoptimeline
		%%% 
		
		%%% 
		\addheadertext{Professional Experience}
		\starttimeline 
			%%
			\timelineitem{2018 -- }{
				Lecturer \\ 
				School of Mathematics and Statistics \\ 
				University of Melbourne, Australia
			}
			\timelinespacer	
			%%
			\timelineitem{2016 -- 2018}{
							Assistant Professor \\ 
							Division of Biostatistics \\ 
							University of Minnesota, Twin Cities
			}
			\timelinespacer
			%%
			\timelineitem{2014 -- 2015}{
							Postdoctoral Researcher\\ 
							Institute of Mathematics \\
							\'{E}cole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL), Switzerland \\ 
							Advisor: Victor Panaretos
			}
			\stoptimeline
	
		%%% 

		\addheadertext{Preprints}
		\nocite{*}
		\printbibliography[heading=none, keyword = {preprint}, env=nodis]
		
		\addheadertext{Publications}
		\nocite{*}
		\printbibliography[heading=none,keyword={Accepted},env=nodis]
	
		%%% 
%		\addheadertext{In revision}
%		\nocite{*}
%		\printbibliography[heading=none, keyword ={revision}, env=nodis]




%		\addheadertext{In preparation}
%		\nocite{*}
%		\printbibliography[heading=none, keyword = {prep}, env=nodis]
%

		%%%
		\addheadertext{Honors and Awards}
		\starttimeline		
		\timelineitem{2019-2021}{
			 Discovery Early Career Researcher Award (DECRA) 
			\begin{itemize}
				\item  Australian Research Council (ARC)
			\end{itemize}
		}
		\timelinespacer
		\timelineitem{2018}{
			Andrew Sisson Fund
			\begin{itemize}
				\item  University of Melbourne
			\end{itemize}
		}
		\timelinespacer
		\timelineitem{2014}{
			Institute of Mathematical Statistics (IMS) Travel Award
			\begin{itemize}
				\item IMS Annual Meeting 
			\end{itemize}
		}
		\timelinespacer
		\timelineitem{2013}{
		Student Travel Grant
			\begin{itemize}
				\item 10th International Conference on Health Policy Statistics \\
			\end{itemize}
		NSF Graduate Research Opportunities Worldwide Award
			\begin{itemize}
				\item Provided funding for research visit to the University of Tromso, Norway \\
			\end{itemize}		
		Student Paper Award
			\begin{itemize}
				\item American Statistical Association Section on Statistical Learning and Data Mining 
			\end{itemize}			
		}
		\timelinespacer
		\timelineitem{2011--2014}{
		NSF Graduate Research Fellowship
			\begin{itemize}
				\item Highly competitive three-year grant providing stipend, tuition and travel funds 
			\end{itemize}
		}
		\timelinespacer{
		\timelineitem{2004--2008}{
		Regents' and Chancellor's Scholar at University of California at Berkeley
			\begin{itemize}
				\item Top 1 percent of incoming freshmen are invited to interview 
			\end{itemize}
	}
		\stoptimeline
			
				
					
		%%% 
		\addheadertext{Presentations in Conferences/Workshops}
		\begin{itemize}
			\item \textit{WNAR}, "The Change-Plane Cox Model" (Invited), Santa Fe, New Mexico, June 2017
			\item \textit{Workshop on Functional Data Analysis}, ``Empirical Evolution Equations" (Invited), Les Diablerets, Switzerland, May 2016
			\item \textit{SIAM Conference on Uncertainty Quantification},``Empirical Evolution Equations" (Contributed), Lausanne, Switzerland, April 2016
			\item \textit{8th International Conference of the ERCIM WG on Computational and Methodological Statistics}, ``Empirical Evolution Equations'' (Invited), London, UK, December 2015
			\item \textit{Methodological advances in Statistics related to Big Data}, ''Empirical Evolution Equations'' (Contributed), Castro Urdiales, Spain, June 2015
			\item \textit{2014 IMS Annual Meeting}, "Latent Supervised Learning for Treatment Effect Heterogeneity" (Contributed), Sydney, Australia, July 2014
			\item \textit{The 3rd Institute of Mathematical Statistics Asia Pacific Rim Meeting},''DiProPerm'' (Invited), Taipei, Taiwan, June 2014
			\item \textit{2014 ENAR Spring Meeting}, "Latent Supervised Learning for Treatment Effect Heterogeneity" (Contributed), Baltimore, Maryland, May 2014
			\item \textit{10th International Conference on Health Policy Statistics}, "Latent Supervised Learning for Survival Data" (Poster), Chicago, Illinois, October 2013
			\item \textit{Joint Statistical Meeting}, "Latent Supervised Learning" (Contributed),  Montreal, Canada, August 2013
		\end{itemize}
				
		%%% 
		\addheadertext{Invited Seminars and Presentations}
		\begin{itemize}
			%\item Empirical Evolution Equations. Department of Mathematics, Statistics, and Computer Science, St. Olaf College (2018).
			\item Reinforcement learning for functional state spaces with application to Type 1 Diabetes. Women in Data Science (WiDS) Conference, Institute for Mathematics and its Applications (IMA) (2018).
			\item Empirical Evolution Equations. Department of Computer Science and Engineering, University of Minnesota (2018).
			\item Empirical Evolution Equations. Department of Mathematics and Statistics, University of Melbourne (2017).
			\item Empirical Evolution Equations. Department of Statistics, University of California Riverside (2017).
			\item Empirical Evolution Equations. Department of Statistics, University of Minnesota (2016).
			\item Introduction to Machine Learning. Nestl\'{e} Institute of Health Sciences, Lausanne (2014).
			\item Latent Supervised Learning. Institute of Mathematics, \'{E}cole Polytechnique F\'{e}d\'{e}rale de Lausanne, Lausanne (2014).
			\item Latent Supervised Learning. Department of Statistics and Applied Probability, University of California at Santa Barbara (2013).					
			\item Latent Supervised Learning. Department of Statistics, University of Pittsburgh (2013).								
			\item Latent Supervised Learning. Department of Biostatistics, University of Pittsburgh (2013).							
			\item Latent Supervised Learning. Division of Biostatistics, University of Minnesota (2013).				
			\item Latent Supervised Learning. Division of Biostatistics, Yale University (2013).		
			\item Latent Supervised Learning. School of Mathematical Sciences, Ohio State University (2013).
			\item Latent Supervised Learning. Department of Statistics, University of California at Davis (2013).		
			\item Latent Supervised Learning. Department of Statistics and Applied Probability, National University of Singapore (2013).
			\item Latent Supervised Learning. Department of Economics, University of Mannheim (2013).
			\item Latent Supervised Learning. School of Mathematical Sciences, University of Nottingham (2013).
		\end{itemize}
		
		
		%%% 
		\addheadertext{Research Experience}
		\starttimeline
			%%
			\timelineitem{Summer 2013}{
			Visiting Researcher \\
			Tromso Telemedicine Laboratory, Norway
			}
			\timelinespacer
			%%
			\timelineitem{2009--2013}{
			Research Assistant \\
			Melanoma Group, University of North Carolina at Chapel Hill
			}
			\timelinespacer
			%%
			\timelineitem{Summer 2010}{
			Research Assistant \\
			School of Dentistry, University of North Carolina at Chapel Hill			
			}
			\timelinespacer			
			%%
			\timelineitem{Summer 2008}{
			Research Experience for Undergraduates (REU) participant \\
			Program on geometric group theory, University of Illinois at Urbana-Champaign
			}
%			\timelinespacer
		\stoptimeline
		
		%%% 
		\addheadertext{Teaching Experience}
		\starttimeline
			\timelineitem{2016-2018}{
				Instructor, University of Minnesota
				\begin{itemize}
					\item {Advanced Statistical Inference (PhD course) Spring 2017 and 2018}
					\item {Advanced Regression and Design (PhD/MS course) Spring 2018}
				\end{itemize}
			}
			\timelinespacer
			%%
			\timelineitem{Fall 2014}{
			Instructor, \'{E}cole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL)
			\begin{itemize}
						\item {Principles of Statistical Inference (PhD course), co-taught with Anthony Davison}
			\end{itemize}
			}
			\timelinespacer
			%%
			\timelineitem{2009--2010}{
			Instructional Assistant, University of North Carolina at Chapel Hill 
			\begin{itemize}
						\item {Statistics, Fall 2009, Professor Ross Leadbetter}
						\item {Statistics, Spring 2010, Professor Shankar Bhamidi}					
			\end{itemize}
			}
			\timelinespacer
			%%
			\timelineitem{2007--2008}{
			Undergraduate Student Instructor, University of California at Berkeley
			\begin{itemize}
						\item {Calculus, Spring 2007, Professor Ole Hald}
						\item {Linear Algebra, Fall 2007, Professor Ming Gu}
						\item {Statistics, Spring 2008, Professor Roger Purves}
						\item {Statistics, Fall 2008, Professor Ani Adhikari}
			\end{itemize}
			}
			\timelinespacer
			%%
			\timelineitem{2004--2007}{
				DeCal Course Instructor, University of California at Berkeley 
				\begin{itemize}
						\item The DeCal program is a collection of student-created and student-run courses at the University of California at Berkeley 
						\item Created and taught class on the mathematics of the Rubik's Cube
				\end{itemize}
			}
			\timelinespacer
		\stoptimeline
		
		
%		\addheadertext{Students supervised}
%		\begin{itemize}
%			\item ???
%		\end{itemize}
		

		
		
		
		%%% 
		\addheadertext{Professional Services}
		\begin{itemize}
			\item In 2016, represented the University of Minnesota in support of an USAID-sponsored one-year Masters of Public Health degree at Hanoi Medical University, Vietnam
			\begin{itemize}
				\item Helped pilot the statistics course 
			\end{itemize}
			\item Reviewer for Biometrika, the Journal of the Royal Statistical Society, the Journal of Machine Learning Research; the Journal of Multivariate Analysis; Computational Statistics and Data Analysis
			\item Contributor to HealthNewsReview.org
			\item Committees
				\begin{itemize}
				\item Diversity Equity Action Leadership Team, School of Public Health, University of Minnesota (2016-2018)
				\item Doctoral Dissertation Fellowship, School of Public Health, University of Minnesota (2016-2018)
				\item Exam committee, Division of Biostatistics, University of Minnesota (2016-2018)
				\item Recruiting committee, Division of Biostatistics, University of Minnesota (2016-2018)
				\item MSc Data Science Curriculum committee, School of Mathematics and Statistics (2018-present)
				\item Diversity and Inclusion committee, , School of Mathematics and Statistics (2018-present)
				\end{itemize}
		\end{itemize}
		
		\addheadertext{Student Supervision}
		\begin{itemize}
			\item Master's students
			\begin{itemize}
				\item Alexandre Mosching, \'{E}cole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL) (2016)
				\item John Ery, \'{E}cole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL) (2015)
			\end{itemize}			
			\item PhD students
			\begin{itemize}
				\item Hui Li, University of Melbourne (2018 to present)
			\end{itemize}
		\end{itemize}
		
		%% 
		\addheadertext{Work Experience}
		\starttimeline
			\timelineitem{2007--2008}{
				Quantitative analyst, Weatherbill, San Francisco, CA
			}
			\timelinespacer

			\timelineitem{Summer 2007}{
				Actuarial intern, Mercer Human Resource Consulting, San Francisco, CA
			}
			\timelinespacer

			\timelineitem{Summer 2006}{
				Quality assurance intern, Omneon Video Networks, Sunnyvale, CA
			}
			\timelinespacer
		\stoptimeline
		
		%%% 
		\addheadertext{Professional Memberships}
		\begin{itemize}
			\item American Statistical Association (2012--present)
			\item Eastern North American Region, International Biometric Society (2012--present)
			\item Institute of Mathematical Sciences (2012--present)
		\end{itemize}
	

	

		
	
		%\newpage
		%%%
		\addheadertext{References}
	\begin{tabular}{lr}
\\
\begin{minipage}[t]{3in}
Michael R. Kosorok (PhD advisor)\\
Department of Biostatistics \\
University of North Carolina \\
Chapel Hill, NC 27599\\
\Telefon\ +1 919 966 8107\\
\Letter\ \href{mailto:kosorok@bios.unc.edu}{kosorok\textrm{@}bios.unc.edu}
\end{minipage}
&
\begin{minipage}[t]{3in}
Fred Godtliebsen\\
Faculty of science and technology \\
Department of Mathematics and Statistics \\
Arctic University of Norway (formerly University of Troms\o)\\
Troms\o, Norway\\
\Telefon\ +47 776 44019\\
\Letter\ \href{mailto:fred.godtliebsen@uit.no}{fred.godtliebsen@\textrm{@}uit.no}
\end{minipage}
\\
\\
\\
\begin{minipage}[t]{3in}
J.S. Marron (PhD advisor) \\
Department of Statistics and Operations Research \\
University of North Carolina \\
Chapel Hill, NC 27599\\
\Telefon\ +1 919 962 2188\\
\Letter\ \href{mailto:marron@unc.edu}{marron\textrm{@}unc.edu}
\end{minipage}
&
\begin{minipage}[t]{3in}
Victor Panaretos \\
Institute of Mathematics \\
\'{E}cole Polytechnique F\'{e}d\'{e}rale de Lausanne \\
Lausanne, Switzerland\\
\Telefon\ +41 21 69 32597\\
\Letter\ \href{mailto:victor.panaretos@epfl.ch}{victor.panaretos\textrm{@}epfl.ch}
\end{minipage}


\end{tabular}
	\end{document}